The Constant-Q Transform Spectral Envelope Coefficients: a musically-adapted timbre feature

### 2021-05-17 IEEE SP Magazine/05-2021 - Draft/article.tex
Worked a bit more on the intro.

\IEEEPARstart{T}{imbre} is the attribute of sound which makes, for example, two musical instruments playing the same note sound different. It is generally associated with the spectral (but also temporal) envelope and is typically assumed to be independent from the pitch (but also the loudness) of the sound \cite{moore2004}. This article will show how to derive a simple but ... timbre feature ...

\cite{brown1991}, \cite{brown1992}
\cite{engel2017}: NSynth

>>>>

\IEEEPARstart{T}{imbre} is the attribute of sound which makes, for example, two musical instruments playing the same note sound different. It is generally associated with the spectral (but also temporal) envelope and is typically assumed to be independent from the pitch (but also the loudness) of the sound \cite{moore2004}. While a complex concept to encompass, this article will show how to compute a simple but representative timbre feature ... well-adapted to musical data.

The feature will be derived from the constant-Q transform (CQT), a log-scaled frequency transform better adapted to musical data \cite{brown1991}, \cite{brown1992}.

The CQT-SEC will compare with the mel-frequency cepstral coefficients (MFCC), on the NSynth dataset, a publicly-available dataset of musical notes \cite{engel2017}.
